Gsmodutils: A python based framework for test driven genome scale metabolic model development

### 2018-02-26 article/article.tex
article names
changes to article

\title{Gsmodutils: A python based framework for test driven genome scale metabolic model development}
\author[1]{James Gilbert}
\author[1]{Nicole Pearcy}
\author[2]{Jamie Twycross}
\affil[1]{Synthetic Biology Research Centre, University of Nottingham, Nottingham, NG7 2RD, United Kingdom}
\affil[2]{Intelligent Modelling and Analysis group, School of Computer Science, University of Nottingham, Nottingham, NG7 2RD, United Kingdom}

@@

\begin{abstract}
\textbf{Motivation:} Genome scale metabolic models are increasingly important for systems biology and metabolic engineering research as they are capable of simulating complex steady state phenotypic behaviour.
Constraints based models of this form can include thousands of reactions and metabolites, with many crucial pathways that only become activated in specific simulation settings.
However, despite their widespread use, power and the availability of tools to aid with the construction and analysis of large scale models little methodology is suggested for the management of continually curated large scale models.
This is quickly becoming an issue for industrial systems and synthetic biotechnology applications, which require good quality reusable models integral to the design, build and test cycle.
\\
\textbf{Results:} Taking advantage of python and cobrapy integration, we have developed the \textit{gsmodutils} modelling framework.
As a fully documented python API and series of command line utilities, gsmodutils places an emphasis on test driven design of models through easy to write test cases in json or python.
Crucially, different substrate conditions are configurable allowing users to examine how different designs or curation impact a wide range of system behaviours, hopefully, minimising error between model versions.
Furthermore, a core feature of the software is to allow users to easily create shareable, self contained, docker images that can be run in cross platform environments.\\
\textbf{Availability:} The software framework described within this paper is open source and freely available from http://github.com/gsmodutils \\
\textbf{Contact:}{james.gilbert@nottingham.ac.uk}
\end{abstract}

@@

\end{document}

>>>>

\title{Gsmodutils: A python based framework for test driven genome scale metabolic model development}
\author[1]{James Gilbert}
\author[1]{Nicole Pearcy}
\author[2]{Jamie Twycross}
\author[3]{John King}
\author[1]{Nigel Minton}
\affil[1]{Synthetic Biology Research Centre, University of Nottingham, Nottingham, NG7 2RD, United Kingdom}
\affil[2]{Intelligent Modelling and Analysis group, School of Computer Science, University of Nottingham, Nottingham, NG7 2RD, United Kingdom}
\affil[3]{School of Mathematical Sciences, University of Nottingham, Nottingham, NG7 2RD, United Kingdom}

@@

\begin{abstract}
\textbf{Motivation:} Genome scale metabolic models are increasingly important for systems biology and metabolic engineering research as they are capable of simulating complex steady state phenotypic behaviour.
Constraints based models of this form can include thousands of reactions and metabolites, with many crucial pathways that only become activated in specific simulation settings.
However, despite their widespread use, power and the availability of tools to aid with the construction and analysis of large scale models little methodology is suggested for the management of continually curated large scale models.
This is quickly becoming an issue for industrial systems and synthetic biotechnology applications, which require good quality reusable models integral to the design, build and test cycle.
\\
\textbf{Results:} 
As part of an ongoing effort to improve genome scale metabolic analysis, we have developed a test driven development methodology for the continuous integration of validation data from different sources.
Contributing to the open source technology based around cobrapy, we have developed the \textit{gsmodutils} modelling framework placing an emphasis on test driven design of models through defined test cases.
Crucially, different substrate conditions are configurable allowing users to examine how different designs or curation impact a wide range of system behaviours, minimising error between model versions.\\
\textbf{Availability:} The software framework described within this paper is open source and freely available from http://github.com/nottingham\_sbrc/gsmodutils \\
\textbf{Contact:}{james.gilbert@nottingham.ac.uk}
\end{abstract}

@@

\end{document}
\grid
